Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-19 chi2012.tex
shortening

We based our two tasks on choosing a university and picking a restaurant for a large social event, because in PS.1 the majority of people stated that they had used multiple websites for these tasks. We used different two different variables for both tasks, where the restaurant was located (Glasgow and Cambridge) and which subject people chose (sport science and history). For the restaurant task, we chose the top restaurants in Glasgow and Cambridge from Tripadvisor and Yelp as the candidates. We chose these cities because they are not geographically close to the participants, to minimise bias). For the university condition we selected two university courses at random, and selected the top six universities for each subject. We selected a shortlist of six because it is typical for users to narrow down their options because analysing the final details of their choice.

>>>>

% why? why were these tasks selected? can we drop in the phrase ``multi-dimensional subjective choice task'' and refer back to PS.1 to justify the choice of tasks?
We based our two tasks on choosing a university and picking a restaurant for a large social event, because in PS.1 the majority of people stated that they had used multiple websites for these tasks.  We used different two different variables for both tasks, where the restaurant was located (Glasgow and Cambridge) and which subject people chose (sport science and history).  For the restaurant task, the cities Glasgow and Cambridge were chosen because they were geographically distant to participants, and would therefore minimise likelihood of prior familiarity with the restaurants or location.  For the University selection task, two university courses were selected at random from the complete university guide\footnote{The Complete University Guide:\\\url{www.thecompleteuniversityguide.co.uk}}, and the six, top-ranked universities for each subject were selected as candidates.  In both tasks, we kept the number of candidate choices at six because we felt it was typical for users to narrow down their options to a limited selection before analysing the details of their final choice.
